\documentclass{wustlthesis}

\setmainfont{Times New Roman}               % Use Times New Roman
\setmathfont{STIXTwoMath}[math-style=ISO]   % Use math font that matches Times New Roman

% Re-calculate the lengths of a text line using the current font
\setlxvchars[\normalfont\normalsize]
\setxlvchars[\normalfont\normalsize]
\checkandfixthelayout[classic]

% Hyperlinks
\usepackage{hyperref}
\hypersetup{%
    colorlinks=true,
    linkcolor=black, urlcolor=blue, citecolor=black%
}

% Tables
\usepackage{threeparttable}
\usepackage{makecell}  % allow multiple lines in a table cell

% Graphics
\usepackage{graphicx}

% Bibliography
\usepackage[
    backend=biber,
    style=nature,
    date=year,
    isbn=false, url=false, doi=true,
    minnames=1, maxnames=9,
    backref=true
]{biblatex}
% rename bibliography section name
\DefineBibliographyStrings{english}{
    bibliography = {References},
    backrefpage = {cited on p\adddot},
    backrefpages = {cited on pp\adddot}}
\urlstyle{same}

% define the bibliography path
\addbibresource{references.bib}


% Configure title page
\settitle{A Mock Thesis on the Proper Formatting of Dissertations and Theses for\\ Arts \& Sciences Graduate Students}
\setauthor{Paige Turner}
\setthesistype{Dissertation}
\setthesisdegree{Doctor of Philosophy}
\setthesisdegreeabbrv{Ph.D.}
% Degree officially earn date must be in December, May, or August
\setdegreeearnmonth{May}
\setdegreeearnyear{2017}
\setthesisadvisor{%
    Katherine Davidsen, Chair\\
    Michael Randolf, Co-Chair}
\setthesiscommittee{%
    Katherine Davidsen, Chair\\
    Michael Randolf, Co-Chair\\
    Richard Lewis\\
    Hillary O’Connell\\
    Jack Taylor}
\setthesisschool{Division of Biology and Biomedical Sciences}
\setthesisdepartment{Neurosciences}


% Optional packages that are not required in the real thesis
\usepackage{layout}     % Show page layout
\usepackage{pifont}     % Extra symbols (optional if the main font has the symbols)


\begin{document}

\thetitlepage                       % Title page
\frontmatter
\thesiscopyright{%                  % Thesis copyright page
    \textcopyright~\degreeearnyear, Paige Turner}

\SingleSpacing*
\setSingleSpace{1.15}
\tableofcontents*                   % Table of contents (ToC)
\listoffigures                      % List of figures (LoF)
\listoftables                       % List of tables (LoT)

\DoubleSpacing
\include{acknowledgments}    % Acknowledgements
\thesisdedication{%                 % Dedication page
    Dedicated to my parents.}

\begin{abstract}
After removing these comments, begin typing the body of your abstract here, double-spaced.  Your
font should be 12-point (which is the text of this sample paragraph). No part of the abstract
should be bolded. If this is for your master's degree, be sure to change all occurrences of the word
``dissertation'' to display as ``thesis,'' and change ``Doctor of Philosophy'' or ``Doctor of
Liberal Arts'' to ``Master of Arts,'' ``Master of Liberal Arts,'' or ``Master of Fine Arts,''
whichever applies.  In the abstract heading above, make sure you use the year your degree is to be
officially earned. Be sure to use your full name as it is recorded in WebSTAC, your dissertation or
thesis advisor's full name(s) wherever appropriate, and the correct title of your degree whenever
referencing it.  The title of your degree will not always be the same as the title of your
department or program, so please check with your departmental administrative assistant and
advisor(s) to be sure you are using the correct degree title.  Please note that an abstract is
required for all dissertation submissions in ProQuest. An abstract is optional for master's thesis
submissions.
\end{abstract}

\mainmatter
\pagestyle{main}
\include{chapters/structure}

\begin{SingleSpace}
\printbibliography
\nocite{*}
\end{SingleSpace}

\appendix
% \include{appendix}

\end{document}
